Responsible Machine Learning\\\large{with Interpretable Models, Post-hoc Explanation, and Disparate Impact Testing}

### 2019-11-06 article-information-2019.tex
fix all the typos I made when rushing before meeting

% Authors, for the paper (add full first names)
\Author{Navdeep Gill $^{1, \dagger}$, Patrick Hall $^{1,\dagger,*}$, Kim Montgomery $^{1,\dagger}$, and Nicholas Schmidt $^{2, \dagger}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad H2O.ai\\
$^{2}$ \quad BLDS, LLC}

>>>>

% Authors, for the paper (add full first names)
\Author{Navdeep Gill $^{1, \dagger}$, Patrick Hall $^{1,3,\dagger,*}$, Kim Montgomery $^{1,\dagger}$, and Nicholas Schmidt $^{2, \dagger}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad H2O.ai\\
$^{2}$ \quad BLDS, LLC\\
$^{3}$ \quad George Washington University}
